Ce que j'ai compris jusqu'à maintenant\\Début de rapport ?

### 2025-04-04 article_bihom_v2.tex
ajout de def semi-regularité et indice de regularité

% !TXS template
\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[a4paper]{geometry}
\usepackage{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage[backend=bibtex]{biblatex}
\usepackage{csquotes}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{hyperref}

@@

		\subsection{Gröbner basis algorithms}
		Gröbner basis algorithms are used to find solutions for polynomial systems using algebraic geometry tools. For a gentle introduction to this subject \cite{CLS}.

@@

		\begin{definition}
			Let $\prec$ be an admissible monomial ordering on a given ring $R = \mathbb{K}[x_1,\dots,x_n]$ where $\mathbb{K}$ is a field. Given a sequence of homogeneous (resp. affine) polynomials $\mathcal{F} = (f_1,\dots,f_m) \in R$, we associate to it the Macaulay matrix of degree $D$ (resp. $\leq D$), denoted by $\Mac{D}{m}{\mathcal{F}}$ (resp. $\Mac{\leq D}{m}{\mathcal{F}}$), and defined as follows: the columns of the matrix are indexed by the monomials of degree $D$ (resp. $\leq D$) sorted in decreasing order from the left to right using the defined monomial ordering. Each row of the matrix is labeled by a tag, also called signature, ($u, f_i$) where u is a monomial in $R$ and $f_i \in \mathcal{F}$ such that $deg(uf_i) = D$ (resp. $deg(uf_i) \leq D$), and the polynomial $uf_i$ is written as vector of coefficients of monomials on the row. We denote by $\Mact{D}{m}{F}$ (resp. $\Mact{\leq D}{m}{F}$) the Macaulay matrix on which we apply the row echelon form without swapping columns to preserve the monomial ordering.
		\end{definition}

@@

>>>>

% !TXS template
\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[a4paper]{geometry}
\usepackage{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage[backend=bibtex]{biblatex}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{hyperref}
\usepackage{lmodern}
\usepackage{csquotes}

@@

		\subsection{Gröbner basis algorithms}
		In the following of the paper we will denote $R = \mathbb{K}[x_1,\dots,x_n]$ a polynomial ring on a field $\mathbb{K}$.

		Gröbner basis algorithms are used to find solutions for polynomial systems using algebraic geometry tools. For a gentle introduction to this subject \cite{CLS}.

@@

		\begin{definition}
			Let $\prec$ be an admissible monomial ordering on a given ring $R$. Given a sequence of homogeneous (resp. affine) polynomials $\mathcal{F} = (f_1,\dots,f_m) \in R$, we associate to it the Macaulay matrix of degree $D$ (resp. $\leq D$), denoted by $\Mac{D}{m}{\mathcal{F}}$ (resp. $\Mac{\leq D}{m}{\mathcal{F}}$), and defined as follows: the columns of the matrix are indexed by the monomials of degree $D$ (resp. $\leq D$) sorted in decreasing order from the left to the right using the defined monomial ordering. Each row of the matrix is labeled by a tag, also called signature, ($u, f_i$) where u is a monomial in $R$ and $f_i \in \mathcal{F}$ such that $deg(uf_i) = D$ (resp. $deg(uf_i) \leq D$), and the polynomial $uf_i$ is written as vector of coefficients of monomials on the row. We denote by $\Mact{D}{m}{F}$ (resp. $\Mact{\leq D}{m}{F}$) the row echelon form of $\Mac{D}{m}{F}$ (resp. $\Mac{\leq D}{m}{F}$) without swapping the columns to mantain the monomial order.
		\end{definition}

@@

		\begin{definition}
			The Hilbert function of a homogeneous ideal $I = \langle f_1,\dots f_m \rangle$ at degree $s$ is defined as
			$$
				HF_{s, m, d}(n) = dim(R/I)_s = dim((R)_s/I_s) = dim(R)_s - dim(I)_s
			$$
			where $d = (d_1,\dots,d_m)$ and $d_i$ is the degree of the homogeneous polynomial $f_i$.
		\end{definition}

		The index of regularity is when this function of $s$ is equal to Hilbert's polynomial of $s$. The degree of this polynomial is exactly the dimension of the ideal. We denote by $H(I)$ the index of regularity of $I$.

		\begin{definition}[Semi-regularity \cite{Bardet04}]
			Let $R = \mathbb{K}[x_1,\dots,x_n]$ a polynomial ring with $\mathbb{K}$ a field.
			A homogeneous sequence $f_1,\dots,f_m \in R$ is semi-regular if the following conditions are verified
			\begin{itemize}
				\item $I = \langle f_1,\dots,f_m \rangle \neq R$
				\item For $i \in [1;m]$, if $g_if_i = 0$ in $R/\langle f_1,\dots,f_m \rangle$ and $deg(g_if_i) < H(I)$ then $g_i = 0$ in $R/\langle f_1,\dots,f_m \rangle$.
			\end{itemize} 
		\end{definition}
